Relationship between solar wind, $D_{st}$, and plasmasphere trough mass density on one-hour time scales

### 2016-02-26 paper.tex
Updates in data section

The parameters $\rho_{eq}$ and $F_{10.7}$ used in this work are from the dataset associated with \cite{Denton}, with data available from 1980 through 1991; all other parameters are from \cite{Reconstruction} over the time range of 1972 through 2013, which are on a 1--hour time grid. $\rho_{eq}$ is the inferred equatorial mass density based on the 3rd harmonic torodial frequency of magnetic field measurements.  The smallest cadence for $\rho_{eq}$ values is 10 minutes.  To compute an hourly average over the same interval for which the solar wind parameters were averaged, the median of all $\rho_{eq}$ values in a given hourly range was used.  Fill values were used for hours in which no measurements were available.  In cases where $\rho_{eq}$ was available from multiple Geostationary Operational Environmental Satellites (GOES) satellites at the same time in the \cite{Denton} dataset, the value from GOES 6 was selected.  In the dataset, measurements from GOES 6 had the longest time span of coverage.  An overview of the data is shown in Figure~\ref{AllData}.

@@

% Though this may skew the onset time slightly, it's thought to be less skewed than trying to determine start and end times with the NaNs in place. This interpolation was only used for determining storm times, and not for any analysis.
% If you say this, you need to do an experiement.  A review will say ``seems like it is an easy statement to check.  Why didn't you?''

>>>>

The parameters $\rho_{eq}$ and $F_{10.7}$ used in this work are from the dataset associated with \cite{Denton}, with data available from 1980 through 1991; all other parameters are from \cite{Reconstruction} from 1972 through 2013, which are on a 1--hour time grid. $\rho_{eq}$ is the inferred equatorial mass density based on the 3rd harmonic torodial frequency of magnetic field measurements.  The smallest cadence for $\rho_{eq}$ values is 10 minutes.  To compute an hourly average over the same interval for which the solar wind parameters were averaged, the median of all $\rho_{eq}$ values in a given hourly range was used.  Fill (NaN) values were used for hours in which no measurements were available.  In cases where $\rho_{eq}$ was available from multiple Geostationary Operational Environmental Satellites (GOES) satellites at the same time in the \cite{Denton} dataset, the value from GOES 6 was selected.  In the dataset, measurements from GOES 6 had the longest time span of coverage.  An overview of the data is shown in Figure~\ref{AllData}.

@@
